Equivalent Income Outcome Visualisation

### 2023-08-15 minos/outcomes/equivalent_income_out.Rmd
Additions to equivalent income visualisation script

```{r}
equivalent_income_comparison_fullpop(base.dat, allchild.dat, 'allChild', save=TRUE, save.path = '/home/luke/Documents/WORK/MINOS/Minos/plots/Equivalent_Income/')
equivalent_income_comparison_fullpop(base.dat, pov.dat, 'povertyChild', save=TRUE, save.path = '/home/luke/Documents/WORK/MINOS/Minos/plots/Equivalent_Income/')
equivalent_income_comparison_fullpop(base.dat, wage.dat, 'LivingWage', save=TRUE, save.path = '/home/luke/Documents/WORK/MINOS/Minos/plots/Equivalent_Income/')
equivalent_income_comparison_fullpop(base.dat, energy.dat, 'EnergyDownlift', save=TRUE, save.path = '/home/luke/Documents/WORK/MINOS/Minos/plots/Equivalent_Income/')

@@

```{r}
base.subset <- base.dat %>%
  select(pidp, time, equivalent_income, alive, weight) %>%
  filter(alive != 'dead') %>%
  group_by(time) %>%
  summarise(equivalent_income = weighted.mean(equivalent_income, w = weight))
base.subset$scenario <- 'Baseline'

@@

@@

```{r}
equivalent_income_comparison_treated(base.dat, allchild.dat, 'allChild', save=TRUE, save.path = '/home/luke/Documents/WORK/MINOS/Minos/plots/Equivalent_Income/')
equivalent_income_comparison_treated(base.dat, pov.dat, 'povertyChild', save=TRUE, save.path = '/home/luke/Documents/WORK/MINOS/Minos/plots/Equivalent_Income/')
equivalent_income_comparison_treated(base.dat, wage.dat, 'LivingWage', save=TRUE, save.path = '/home/luke/Documents/WORK/MINOS/Minos/plots/Equivalent_Income/')
equivalent_income_comparison_treated(base.dat, energy.dat, 'EnergyDownlift', save=TRUE, save.path = '/home/luke/Documents/WORK/MINOS/Minos/plots/Equivalent_Income/')

@@

>>>>

```{r}
equivalent_income_comparison_fullpop(base.dat, allchild.dat, 'allChild')
equivalent_income_comparison_fullpop(base.dat, pov.dat, 'povertyChild')
equivalent_income_comparison_fullpop(base.dat, wage.dat, 'LivingWage')
equivalent_income_comparison_fullpop(base.dat, energy.dat, 'EnergyDownlift')

@@

```{r}
base.subset <- base.batch %>%
  select(pidp, time, equivalent_income, alive, weight) %>%
  filter(alive != 'dead') %>%
  group_by(time) %>%
  summarise(equivalent_income = weighted.mean(equivalent_income, w = weight))
base.subset$scenario <- 'Baseline'

@@

```{r}
base.subset <- base.batch %>%
  select(pidp, time, run_id, equivalent_income, weight) %>%
  group_by(time, run_id) %>%
  summarise(equivalent_income = weighted.mean(equivalent_income, w = weight)) %>%
  mutate(scenario = 'Baseline')

wage.subset <- wage.batch %>%
  select(pidp, time, run_id, equivalent_income, weight) %>%
  group_by(time, run_id) %>%
  summarise(equivalent_income = weighted.mean(equivalent_income, w = weight)) %>%
  mutate(scenario = 'LivingWage')

energy.subset <- energy.batch %>%
  select(pidp, time, run_id, equivalent_income, weight) %>%
  group_by(time, run_id) %>%
  summarise(equivalent_income = weighted.mean(equivalent_income, w = weight)) %>%
  mutate(scenario = 'EnergyCrisis')

all.combined <- rbind(base.subset, wage.subset, energy.subset)
all.combined$scenario <- factor(all.combined$scenario, levels = c('Baseline', 'LivingWage', 'EnergyCrisis'))

ggplot(data = all.combined, aes(x = time, y = equivalent_income, group = scenario, color = scenario)) +
  geom_smooth() +
  labs(title = 'Equivalent Income Comparison', subtitle = 'Whole Population') +
  xlab('Year') +
  ylab('Equivalent Income (£)')
```

@@

```{r}
equivalent_income_comparison_treated(base.dat, allchild.dat, 'allChild')
equivalent_income_comparison_treated(base.dat, pov.dat, 'povertyChild')
equivalent_income_comparison_treated(base.dat, wage.dat, 'LivingWage')
equivalent_income_comparison_treated(base.dat, energy.dat, 'EnergyDownlift')

@@

### CHANGE IN INCOME / EQUIVALENT INCOME
